### 2021-12-13 thesis/tex/nsiResults.tex
Conclusion almost done

For our analyses, we define our $\chi^2$ as
\begin{align}\label{eq:chisq_NSI}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory in bin $\{i,j,k\}$, where $i$ denotes the $\Ereco$ bin, $j$ denotes the $\zreco$ bin,
and $k$ denotes the event-type bin, i.e. track or cascade. 
$N_{ijk}^\text{data}$ is the observed number of events in that bin. $\sigma^\text{data}_{ijk}$ is the experimental uncertainty, and $\sigma^\text{syst}_{ijk}$ the uncorrelated systematic
uncertainty.

@@

After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. 
The results are shown in Fig.~\ref{fig:IC_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}. Each region is bounded
by the best and worst case scenario, as defined in Table~\ref{table:syst_errors}, while the middle line is the baseline scenario. We again emphasize that 
no scenarios are considered for DeepCore, since they already provided in the data release~\cite{DC2019data}.

@@

Using the baseline case of 3\% systematic uncertainty at 90\% CL, we find from Table~\ref{table:PINGU_joint_results}, that our predictions for the proposed PINGU detector are
\begin{align}\label{eq_P_results}
   -0.049 <&\, \ett < 0.057 \nonumber \\
   -0.010 <&\, \emt < 0.011 \nonumber \\
   -0.137 <&\, \eem < 0.11 \nonumber \\
   -0.132 <&\, \eet < 0.125\,,
\end{align}
which displays an improvement over the DeepCore results in Eq.~\ref{eq:DC_results}, except for $\eet$ which is worse.

Finally, the joint results for $\emt$ using IceCube and DeepCore from~\ref{table:PINGU_joint_results} at 90\% CL are
\begin{align}\label{eq:ID_result}
   -0.016 <&\, \emt < 0.0070\,,
\end{align}
and when combining IceCube, DeepCore, and PINGU, the 90\% CL constraint on $\emt$ in our baseline scenario is predicted to be
\begin{align}\label{eq:PID_result}
   -0.010 <&\, \emt < 0.0060\,,
\end{align}
which is more stringent for $\emt>0$ than the result in~\cite{deepcoreNSI}.
\newpage

>>>>

\subsection{$\chi^2$ Minimization}\label{sec:nsi_chi2}
For our analyses, we define our $\chi^2$ as
\begin{align}\label{eq:chisq_NSI}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory in bin $\{i,j,k\}$, where $i$ denotes the $\Ereco$ bin, $j$ denotes the $\zreco$ bin,
and $k$ denotes the event-type bin, i.e. track or cascade. 
$N_{ijk}^\text{data}$ is the observed number of events in that bin. $\sigma^\text{data}_{ijk}$ is the experimental uncertainty, and $\sigma^\text{syst}_{ijk}$ the uncorrelated systematic
uncertainty.

@@

\subsection{Constraining the NSI parameters}\label{sec:constraining_NSI}
After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. 
The results are shown in Fig.~\ref{fig:IC_3D} and summarized in Tables~\ref{table:IC_DC_results} and~\ref{table:PINGU_joint_results}. Each region is bounded
by the best and worst case scenario, as defined in Table~\ref{table:syst_errors}, while the middle line is the baseline scenario. We again emphasize that 
no scenarios are considered for DeepCore, since they already provided in the data release~\cite{DC2019data}.

@@

Using the baseline case of 3\% systematic uncertainty at 90\% CL, we find from Table~\ref{table:PINGU_joint_results}, that our predictions for the proposed PINGU detector are
\begin{align}\label{eq:P_results}
   -0.049 <&\, \ett < 0.057 \nonumber \\
   -0.010 <&\, \emt < 0.011 \nonumber \\
   -0.137 <&\, \eem < 0.11 \nonumber \\
   -0.132 <&\, \eet < 0.125\,,
\end{align}
which displays an improvement over the DeepCore results in Eq.~\ref{eq:DC_results}, except for $\eet$ which is worse.

Finally, the joint results for $\emt$ using IceCube and DeepCore from~\ref{table:PINGU_joint_results} at 90\% CL are
\begin{align}\label{eq:ID_result}
   -0.016 <&\, \emt < 0.0070\,,
\end{align}
and when combining IceCube, DeepCore, and PINGU, the 90\% CL constraint on $\emt$ in our baseline scenario is predicted to be
\begin{align}\label{eq:PID_result}
   -0.010 <&\, \emt < 0.0060\,,
\end{align}
which is more stringent for $\emt>0$ than the result in~\cite{deepcoreNSI}.
